%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Matthew Widdop} % Your name

\address{Birmingham, UK \\ linkedin.com/in/matthew-widdop}% address

\address{REDACTED \\ github.com/MattyTheHacker} % Phone

\address{mrw078@student.bham.ac.uk \\ MattyTheHacker.github.io} % Email

\begin{document}

%----------------------------------------------------------------------------------------
%	PERSONAL STATEMENT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Personal Statement}

I am currently studying a bachelor's degree in Computer Science at the University of Birmingham, currently averaging a first. I am primarily interested in software development, cyber security and networking. I have a clear record showing dedication to improving the student experience throughout the university and making positive change to benefit students and staff alike. My current primary project is the CSS website found at cssbham.com 

\end{rSection}

%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Birmingham, Birmingham} \hfill {\em September 2021 - Present} \\ 
B.Sc. Computer Science\\
- Object Oriented Programming (96\%)\\
- Full Stack Application Development (100\%)\\

{\bf University of Birmingham, Birmingham} \hfill {\em September 2020 - July 2021} \\ 
B.Sc. Engineering \& Physical Sciences Foundation Year\\
- Elementary Computer Programming (99\%) \\

{\bf Craven College, Skipton} \hfill {\em September 2018 - July 2020} \\
Level 3 Extended Diploma in Information Technology (D*D*D*) \\

{\bf South Craven Secondary School, Cross Hills} \hfill {\em September 2013 - July 2018} \\
13 GCSEs Grade 9 to 5(A* to C)

\end{rSection}

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

%------------------------------------------------
\comment{
\begin{rSubsection}{Guild of Students, UoB}{October 2022 - Present}{Security Assistant}{Birmingham, UK}
\item did shit ya know
\end{rSubsection}}

\begin{rSubsection}{School of Computer Science}{September 2022 - Present}{Student Ambassador}{Birmingham, UK}
\item  Provided information and tours to prospective students at open days and offer holder visit days. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Guild of Students, UoB}{September 2022 - Present}{Student Groups Assistant}{Birmingham, UK}
\item Administrative and customer service duties for student societies at UoB.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{MarketicUK}{May 2019 - September 2022}{Accountant}{Leeds, UK}
\item All financial management, reporting and filing for the company. 
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths \& Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & Java, Python, Haskell, C \\
Markup Languages & LaTeX, HTML, CSS, Markdown, PHP, JS, SQL, XML, JSON \\
Protocols \& APIs & REST, SSH, SFTP \\
Databases & MySQL, PostgreSQL \\
OSs & Windows, Ubuntu, Kali, Tails\\
Tools & Git, Visual Studio Code, IntelliJ, Excel, Google Sheets, Jupyter
\end{tabular}
\end{rSection}
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	CERTS, HONOURS, AWARDS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications, Honours and Awards}
\comment{\begin{rSubsection}{Cisco Certified Network Associate}{September 2022}{}{}
\item The CCNA exam covers networking fundamentals, IP services, security fundamentals, automation and programmability. Designed for agility and versatility, CCNA validates that you have the skills required to manage and optimise today's most advanced networks.
\end{rSubsection}}
\begin{rSubsection}{Personal Skills Award (Advanced)}{September 2022}{}{}
\item The Personal Skills Award (PSA) is the University of Birmingham’s optional employability programme, designed to develop professional skills and attributes in preparation for graduate employment. Upon completion of the award, an assessment is undertaken which will demonstrate exceptional commitment to developing skills and fostering professional practice.
\end{rSubsection}
\begin{rSubsection}{Bloomberg Market Concepts}{August 2022}{}{}
\item Bloomberg Market Concepts (BMC) is a self-paced e-learning course that provides an interactive introduction to the financial markets. BMC consists of 3 sections — Core Concepts (includes four modules – Economic Indicators, Currencies, Fixed Income, Equities), Getting Started on the Terminal and Portfolio Management.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	EXTRA CURRICULAR SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Extra Curricular}
\begin{rSubsection}{UoB Sport and Fitness}{October 2022 - Present}{Club Development Executive - Combat Sports}{Birmingham, UK}
\item Worked with the club development executive to represent the views of combat sports clubs.
\end{rSubsection}
\begin{rSubsection}{Guild of Students Activities Committee}{October 2022 - Present}{Student Representative}{Birmingham, UK}
\item Contributed to the strategic plan of the student groups department at the Guild.
\end{rSubsection}

\begin{rSubsection}{University of Birmingham Senate}{June 2022 - Present}{UG Student Representative}{Birmingham, UK}
\item Representing all 25,000 undergraduate students at UoB to the Senate. 
\end{rSubsection}

\begin{rSubsection}{College of Engineering and Physical Sciences, UoB}{June 2022 - Present}{College Representative}{Birmingham, UK}
\item Responsible for representing all 10,000 students within the college of EPS to the college level committees. 
\end{rSubsection}

\begin{rSubsection}{Misconduct and Academic Appeals Committee, UoB}{May 2022 - Present}{Nominated Student}{Birmingham, UK}
\item Considered written and oral evidence as a full member of the committee to make decisions on student cases brought before the committee. 
\end{rSubsection}

\comment{
\begin{rSubsection}{Poker Society, UoB}{April 2022 - Present}{Social Secretary}{Birmingham, UK}
\item Responsible for organising and managing social events for the Poker Society at UoB.
\end{rSubsection}}

\begin{rSubsection}{Jiu-Jitsu Club, UoB}{March 2022 - Present}{Captain}{Birmingham, UK}
\item Responsible for the management and organisation of the Jiu Jitsu club at UoB with more than 55 members and 3 instructors.
\end{rSubsection}

\begin{rSubsection}{Computer Science Society, UoB}{February 2022 - Present}{Industrial Liaison}{Birmingham, UK}
\item Collaborated with industry contacts to secure sponsorship agreements for the society totaling around £5,000 so far, which is approximately 30\% more than at this point last year. 
\end{rSubsection}

\begin{rSubsection}{School of Computer Science, UoB}{October 2021 - Present}{School Representative}{Birmingham, UK}
\item Represtned the views and opinions of all 3,000 students in the SoCS to school level committees.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	REFERENCES SECTION
%----------------------------------------------------------------------------------------

\comment{\begin{rSection}{References}
\begin{multicols}{2}
Name: Lydia Eason\\
Email: l.eason@bham.ac.uk\\
Phone: 07966 277335\\
Relationship: Student Rep Coordinator

\columnbreak

Name: Oliver Yates\\
Email: ollie@marketic.co.uk\\
Phone: 07483 803855\\
Relationship: Director at MarketicUK

\end{multicols}
\end{rSection}}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
